\chapter{Firefox Bug Report} \label{App:Firefox Bug Report}

\begin{preamble}
	An appendix detailing a bug report submitted for the Firefox browser.
\end{preamble}

\section{Introduction}

This is the contents of the bug filed in the Mozilla bug tracker (number 1106045) \citep{FirefoxFocusLoopBug}, reporting the occurrence of ``focus loops'' in certain HTML structures. It was later discovered that these structures were invalid HTML, and so the bug will likely go unfixed.

\section{What did you do?}\label{what-did-you-do}

I was testing a Web application for keyboard accessibility. In the
application there were some HTML structures like the following:

\begin{lstlisting}[language=html]
<a href="#">
    <div>
        The link text
        <button type="button">Button 1</button>
        <button type="button">Button 2</button>
    </div>
</a>
\end{lstlisting}

(I have created a JSFiddle illustrating the problem at
\url{http://jsfiddle.net/jjxuL1tz/5/}.)

I attempted to tab through this structure to focus elements further on
in the HTML.

\section{What happened?}\label{what-happened}

I became stuck in a focus cycle. That is, pressing Tab when Button 2 was
focussed returned focus to the parent
\texttt{\textless{}a\textgreater{}} tag, so the focus went as follows:

\begin{verbatim}
<a> -> Button 1 -> Button 2 -> <a> -> Button 1 -> ...
\end{verbatim}

When \texttt{\textless{}a\textgreater{}} was focussed, I could press
Shift+Tab to get out of the cycle and focus the previous element in the
document, but I could not focus the element after the cycle without
using the mouse.

\section{What should have happened?}\label{what-should-have-happened}

With Button 2 focussed, I should have been able to press Tab to focus
the next element on the page.

\section{Workaround}\label{workaround}

The problem does not occur if the
\texttt{\textless{}button\textgreater{}}s are replaced with
\texttt{\textless{}a\textgreater{}}s; indeed, adding one
\texttt{\textless{}a\textgreater{}} tag as a sibling of the
\texttt{\textless{}button\textgreater{}}s fixes the problem, even if it
has its \texttt{tabindex} attribute set to -1.

An example of this can be found in the JSFiddle
(\url{http://jsfiddle.net/jjxuL1tz/5/}).
