%% ----------------------------------------------------------------
%% AppendixAccessibilityStandards.tex
%% ---------------------------------------------------------------- 
\chapter{Accessibility Standards} 
\label{Chapter:Accessibility Standards}
Both of our example user interfaces were tested against the \gls{WCAG} 2.0 Standards\footnote{\url{http://www.w3.org/TR/WCAG20/} (Accessed: 15 Jan 15)} to check for accessibility.

\section{Videogular Questions Example}
\label{Section: Conformance of Videogular Questions Example}
\begin{longtable}{|L{0.6}|L{0.03}|L{0.28}|} 
\caption{\label{table: vqe conformance}Conformance to WCAG 2.0 Guidelines for Videogular Questions Example} \\
\hline \textbf{Standard} & \rot{\textbf{Pass }} & \textbf{Comment}\\ \hhline{|===|} \endhead
\multicolumn{3}{c}{Continues on the next page...} \endfoot
\endlastfoot
\textbf{1.1 Text Alternatives:} Provide text alternatives for any non-text content so that it can be changed into other forms people need, such as large print, braille, speech, symbols or simpler language. & \XSolidBrush & There is no text alternative for the video but as the idea is to integrate this into Synote giving this feature would cause duplication\eoline
\textbf{1.2 Time-based Media:} Provide alternatives for time-based media. & \XSolidBrush & There are no captions for the video content. This is down to the video uploaded by the user.\eoline
\textbf{1.3.1 Info and Relationships:} Information, structure, and relationships conveyed through presentation can be programmatically determined or are available in text. (Level A) & \CheckmarkBold & All buttons that use symbols have aria-labels \eoline
\textbf{1.3.2 Meaningful Sequence:} When the sequence in which content is presented affects its meaning, a correct reading sequence can be programmatically determined. (Level A) & \CheckmarkBold  &  Sensible read order determined by WAVE toolbar\eoline
\textbf{1.3.3 Sensory Characteristics:} Instructions provided for understanding and operating content do not rely solely on sensory characteristics of components such as shape, size, visual location, orientation, or sound. (Level A) & \XSolidBrush  & Video content relies on sound. As this is for integration into Synote the transcript will be provided there. \eoline
\textbf{1.4.1 Use of Color:} Color is not used as the only visual means of conveying information, indicating an action, prompting a response, or distinguishing a visual element. (Level A) & \XSolidBrush & The cuepoints are only conveyed by a different colour on the scrub bar. Future work could be to add information conveyed in other ways.\eoline
\textbf{1.4.2 Audio Control:} If any audio on a Web page plays automatically for more than 3 seconds, either a mechanism is available to pause or stop the audio, or a mechanism is available to control audio volume independently from the overall system volume level. (Level A) & \CheckmarkBold & Video does not play until play button is clicked. The volume can also be adjusted separately of system volume\eoline
\textbf{1.4.3 Contrast (Minimum):} The visual presentation of text and images of text has a contrast ratio of at least 4.5:1, except for the following: (Level AA) 
\begin{itemize}
\item Large Text: Large-scale text and images of large-scale text have a contrast ratio of at least 3:1;
\item Incidental: Text or images of text that are part of an inactive user interface component, that are pure decoration, that are not visible to anyone, or that are part of a picture that contains significant other visual content, have no contrast requirement.
\item  Logotypes: Text that is part of a logo or brand name has no minimum contrast requirement.
\end{itemize}
 & \CheckmarkBold & All text has an acceptable contrast ratio \eoline
\textbf{1.4.4 Resize text:} Except for captions and images of text, text can be resized without assistive technology up to 200 percent without loss of content or functionality. (Level AA) & \CheckmarkBold & All text can be resized to 200\% without loss of content or functionality\eoline
\textbf{1.4.5 Images of Text:} If the technologies being used can achieve the visual presentation, text is used to convey information rather than images of text except for the following: (Level AA)
\begin{itemize}
\item Customizable: The image of text can be visually customized to the user's requirements;
\item Essential: A particular presentation of text is essential to the information being conveyed.
\end{itemize}
Note: Logotypes (text that is part of a logo or brand name) are considered essential.
& \CheckmarkBold & There are no images of text\\ \hhline{|===|}
\textbf{2.1.1 Keyboard: }All functionality of the content is operable through a keyboard interface without requiring specific timings for individual keystrokes, except where the underlying function requires input that depends on the path of the user's movement and not just the endpoints. (Level A) & \CheckmarkBold & All content is operable using only a keyboard \eoline
\textbf{2.1.2 No Keyboard Trap: }If keyboard focus can be moved to a component of the page using a keyboard interface, then focus can be moved away from that component using only a keyboard interface, and, if it requires more than unmodified arrow or tab keys or other standard exit methods, the user is advised of the method for moving focus away. (Level A)  & \CheckmarkBold & There are no keyboard traps\eoline
\textbf{2.1.3 Keyboard (No Exception): }All functionality of the content is operable through a keyboard interface without requiring specific timings for individual keystrokes. (Level AAA)   & \CheckmarkBold & No specific timings are needed for the keyboard strokes (you can pause then move along the scrub bar rather than having to pause at the correct point).\eoline
\textbf{2.2 Enough Time: }Provide users enough time to read and use content. & \CheckmarkBold & Level AAA as no user interactions are time sensitive \eoline
\textbf{2.3 Seizures: }Do not design content in a way that is known to cause seizures.  & \CheckmarkBold & None of the content flashes. \eoline
\textbf{2.4.1 Bypass Blocks: }A mechanism is available to bypass blocks of content that are repeated on multiple Web pages. (Level A)  & \CheckmarkBold & There is a skip to content link for screen readers\eoline
\textbf{2.4.2 Page Titled:} Web pages have titles that describe topic or purpose. (Level A) & \CheckmarkBold & All pages are titled descriptively \eoline
\textbf{2.4.3 Focus Order:} If a Web page can be navigated sequentially and the navigation sequences affect meaning or operation, focusable components receive focus in an order that preserves meaning and operability. (Level A)  & \CheckmarkBold & The tab order matches the read order \eoline
\textbf{2.4.4 Link Purpose (In Context): }The purpose of each link can be determined from the link text alone or from the link text together with its programmatically determined link context, except where the purpose of the link would be ambiguous to users in general. (Level A) & \CheckmarkBold & Links are obviously to other videos\eoline
\textbf{2.4.5 Multiple Ways:} More than one way is available to locate a Web page within a set of Web pages except where the Web Page is the result of, or a step in, a process. (Level AA)  & \CheckmarkBold & Every page can be found from all pages\eoline
\textbf{2.4.6 Headings and Labels:} Headings and labels describe topic or purpose. (Level AA)  & \CheckmarkBold & Headings and labels are descriptive\eoline
\textbf{2.4.7 Focus Visible:} Any keyboard operable user interface has a mode of operation where the keyboard focus indicator is visible. (Level AA)  & \CheckmarkBold & Keyboard focus is visible (dotted lines)\eoline
\textbf{2.4.8 Location: }Information about the user's location within a set of Web pages is available. (Level AAA)  & \CheckmarkBold & The title shows which of the pages the user is on and there is only one level of navigation \eoline
\textbf{2.4.9 Link Purpose (Link Only): }A mechanism is available to allow the purpose of each link to be identified from link text alone, except where the purpose of the link would be ambiguous to users in general. (Level AAA)  & \CheckmarkBold & Links are all to other videos \eoline
\textbf{2.4.10 Section Headings: }Section headings are used to organize the content. (Level AAA)
\begin{itemize}
\item Note 1: "Heading" is used in its general sense and includes titles and other ways to add a heading to different types of content.
\item Note 2: This success criterion covers sections within writing, not user interface components. User Interface components are covered under Success Criterion 4.1.2.
\end{itemize}
& - & No section headings are needed as content is all in one section \\ \hhline{|===|}
\textbf{3.1.1 Language of Page:} The default human language of each Web page can be programmatically determined. (Level A)  & & \eoline
\textbf{3.2.1 On Focus:} When any component receives focus, it does not initiate a change of context. (Level A)  & \CheckmarkBold & The \texttt{lang} attribute is set to \texttt{en}\eoline
\textbf{3.2.2 On Input:} Changing the setting of any user interface component does not automatically cause a change of context unless the user has been advised of the behavior before using the component. (Level A) & \CheckmarkBold & No settings to change\eoline
\textbf{3.2.3 Consistent Navigation: }Navigational mechanisms that are repeated on multiple Web pages within a set of Web pages occur in the same relative order each time they are repeated, unless a change is initiated by the user. (Level AA)  & \CheckmarkBold & Same navigation on each page\eoline
\textbf{3.2.4 Consistent Identification: }Components that have the same functionality within a set of Web pages are identified consistently. (Level AA) & \CheckmarkBold & All symbols and references are consistent\eoline
\textbf{3.2.5 Change on Request: }Changes of context are initiated only by user request or a mechanism is available to turn off such changes. (Level AAA) & \CheckmarkBold & User needs to click on a link to change the context \eoline
\textbf{3.3 Input Assistance:} Help users avoid and correct mistakes. & \CheckmarkBold & Validation on answers but no help in actually answering the question. Can skip back to certain content if that setting is set\\ \hhline{|===|}
\textbf{4.1.1 Parsing:} In content implemented using markup languages, elements have complete start and end tags, elements are nested according to their specifications, elements do not contain duplicate attributes, and any IDs are unique, except where the specifications allow these features. (Level A) & & \eoline
\textbf{4.1.2 Name, Role, Value:} For all user interface components (including but not limited to: form elements, links and components generated by scripts), the name and role can be programmatically determined; states, properties, and values that can be set by the user can be programmatically set; and notification of changes to these items is available to user agents, including assistive technologies. (Level A) & \CheckmarkBold & Aria roles and marks have been defined \eoline
\end{longtable}

\section{Videogular Analytics Example}
\label{Section: Conformance of Videogular Analytics Example}
\begin{longtable}{|L{0.6}|L{0.03}|L{0.28}|} 
\caption{\label{table: va conformance}Conformance to WCAG 2.0 Guidelines for Videogular Analytics Example} \\
\hline \textbf{Standard} & \rot{\textbf{Pass }} & \textbf{Comment}\\ \hhline{|===|} \endhead
\multicolumn{3}{c}{Continues on the next page...} \endfoot
\endlastfoot
\textbf{1.1 Text Alternatives:} Provide text alternatives for any non-text content so that it can be changed into other forms people need, such as large print, braille, speech, symbols or simpler language. & \XSolidBrush & There is no text alternative for the video.\eoline
\textbf{1.2 Time-based Media:} Provide alternatives for time-based media. & \XSolidBrush & There are no captions for the video content. This is down to the video uploaded by the user.\eoline
\textbf{1.3.1 Info and Relationships:} Information, structure, and relationships conveyed through presentation can be programmatically determined or are available in text. (Level A) & \XSolidBrush & The graphs are not explained in text. However this was a proof-of-concept to show that graphs could be used. The text could be added by a developer\eoline
\textbf{1.3.2 Meaningful Sequence:} When the sequence in which content is presented affects its meaning, a correct reading sequence can be programmatically determined. (Level A) & \CheckmarkBold  & Correct reading sequence is determined by the WAVE toolbar \eoline
\textbf{1.3.3 Sensory Characteristics:} Instructions provided for understanding and operating content do not rely solely on sensory characteristics of components such as shape, size, visual location, orientation, or sound. (Level A) & \XSolidBrush & To understand the graphs you need to be able to see them. Future work could be on the development of accessible graphs \eoline
\textbf{1.4.1 Use of Color:} Color is not used as the only visual means of conveying information, indicating an action, prompting a response, or distinguishing a visual element. (Level A) & \CheckmarkBold & The heat map data is conveyed by a different colour on the scrub bar but also in a table\eoline
\textbf{1.4.2 Audio Control:} If any audio on a Web page plays automatically for more than 3 seconds, either a mechanism is available to pause or stop the audio, or a mechanism is available to control audio volume independently from the overall system volume level. (Level A) & \CheckmarkBold & Video is not playing by default and the volume can be adjusted independently of overall system volume\eoline
\textbf{1.4.3 Contrast (Minimum):} The visual presentation of text and images of text has a contrast ratio of at least 4.5:1, except for the following: (Level AA) 
\begin{itemize}
\item Large Text: Large-scale text and images of large-scale text have a contrast ratio of at least 3:1;
\item Incidental: Text or images of text that are part of an inactive user interface component, that are pure decoration, that are not visible to anyone, or that are part of a picture that contains significant other visual content, have no contrast requirement.
\item  Logotypes: Text that is part of a logo or brand name has no minimum contrast requirement.
\end{itemize}
 & \CheckmarkBold & All colour contrast is of an acceptable ratio\eoline
\textbf{1.4.4 Resize text:} Except for captions and images of text, text can be resized without assistive technology up to 200 percent without loss of content or functionality. (Level AA) & & \eoline
\textbf{1.4.5 Images of Text:} If the technologies being used can achieve the visual presentation, text is used to convey information rather than images of text except for the following: (Level AA)
\begin{itemize}
\item Customizable: The image of text can be visually customized to the user's requirements;
\item Essential: A particular presentation of text is essential to the information being conveyed.
\end{itemize}
Note: Logotypes (text that is part of a logo or brand name) are considered essential.
& \CheckmarkBold & All text can be resized without assistive technology up to 200\% without loss of content or functionality \\ \hhline{|===|}
\textbf{2.1.1 Keyboard: }All functionality of the content is operable through a keyboard interface without requiring specific timings for individual keystrokes, except where the underlying function requires input that depends on the path of the user's movement and not just the endpoints. (Level A) & \CheckmarkBold & All content is completely functional for a keyboard-only user \eoline
\textbf{2.1.2 No Keyboard Trap: }If keyboard focus can be moved to a component of the page using a keyboard interface, then focus can be moved away from that component using only a keyboard interface, and, if it requires more than unmodified arrow or tab keys or other standard exit methods, the user is advised of the method for moving focus away. (Level A)  & \CheckmarkBold & No keyboard traps exist \eoline
\textbf{2.1.3 Keyboard (No Exception): }All functionality of the content is operable through a keyboard interface without requiring specific timings for individual keystrokes. (Level AAA) & \CheckmarkBold & No specific timings are required\eoline
\textbf{2.2 Enough Time: }Provide users enough time to read and use content. & \CheckmarkBold & Level AAA as no user interactions are time sensitive \eoline
\textbf{2.3 Seizures: }Do not design content in a way that is known to cause seizures.  & \CheckmarkBold & No flashing content\eoline
\textbf{2.4.1 Bypass Blocks: }A mechanism is available to bypass blocks of content that are repeated on multiple Web pages. (Level A)  & \CheckmarkBold & Skip to content link is available for screen readers\eoline
\textbf{2.4.2 Page Titled:} Web pages have titles that describe topic or purpose. (Level A) & \CheckmarkBold & All tabs have descriptive titles\eoline
\textbf{2.4.3 Focus Order:} If a Web page can be navigated sequentially and the navigation sequences affect meaning or operation, focusable components receive focus in an order that preserves meaning and operability. (Level A)  & \CheckmarkBold & Tab order matches read order\eoline
\textbf{2.4.4 Link Purpose (In Context): }The purpose of each link can be determined from the link text alone or from the link text together with its programmatically determined link context, except where the purpose of the link would be ambiguous to users in general. (Level A) & \CheckmarkBold & Links are only to switch tabs which are named \eoline
\textbf{2.4.5 Multiple Ways:} More than one way is available to locate a Web page within a set of Web pages except where the Web Page is the result of, or a step in, a process. (Level AA)  &  \CheckmarkBold & All information is in one page \eoline
\textbf{2.4.6 Headings and Labels:} Headings and labels describe topic or purpose. (Level AA)  & \CheckmarkBold & All headings and labels are descriptive \eoline
\textbf{2.4.7 Focus Visible:} Any keyboard operable user interface has a mode of operation where the keyboard focus indicator is visible. (Level AA)  & \CheckmarkBold & The keyboard focus is visible \eoline
\textbf{2.4.8 Location: }Information about the user's location within a set of Web pages is available. (Level AAA) & \CheckmarkBold & All information is on one web page\eoline
\textbf{2.4.9 Link Purpose (Link Only): }A mechanism is available to allow the purpose of each link to be identified from link text alone, except where the purpose of the link would be ambiguous to users in general. (Level AAA)  & \CheckmarkBold & Links are only for switching tabs and roles are defined for the tabs \eoline
\textbf{2.4.10 Section Headings: }Section headings are used to organize the content. (Level AAA)
\begin{itemize}
\item Note 1: "Heading" is used in its general sense and includes titles and other ways to add a heading to different types of content.
\item Note 2: This success criterion covers sections within writing, not user interface components. User Interface components are covered under Success Criterion 4.1.2.
\end{itemize}
& - & No sections headings as sectioning is not required \\ \hhline{|===|}
\textbf{3.1.1 Language of Page:} The default human language of each Web page can be programmatically determined. (Level A) & \CheckmarkBold & The \texttt{lang} attribute is set to \texttt{en} \eoline
\textbf{3.2.1 On Focus:} When any component receives focus, it does not initiate a change of context. (Level A) & \CheckmarkBold & A change of focus does not change the context\eoline
\textbf{3.2.2 On Input:} Changing the setting of any user interface component does not automatically cause a change of context unless the user has been advised of the behavior before using the component. (Level A)  & \CheckmarkBold & User is advised of behaviour in the text by the component\eoline
\textbf{3.2.3 Consistent Navigation: }Navigational mechanisms that are repeated on multiple Web pages within a set of Web pages occur in the same relative order each time they are repeated, unless a change is initiated by the user. (Level AA) & \CheckmarkBold & This is a one page site\eoline
\textbf{3.2.4 Consistent Identification: }Components that have the same functionality within a set of Web pages are identified consistently. (Level AA)  & \CheckmarkBold & All names and references used are consistent\eoline
\textbf{3.2.5 Change on Request: }Changes of context are initiated only by user request or a mechanism is available to turn off such changes. (Level AAA) & \CheckmarkBold & A change of context can only come from a user changing the tab\eoline
\textbf{3.3 Input Assistance:} Help users avoid and correct mistakes.  & - & There is no wrong input\\ \hhline{|===|}
\textbf{4.1.1 Parsing:} In content implemented using markup languages, elements have complete start and end tags, elements are nested according to their specifications, elements do not contain duplicate attributes, and any IDs are unique, except where the specifications allow these features. (Level A) & & \eoline
\textbf{4.1.2 Name, Role, Value:} For all user interface components (including but not limited to: form elements, links and components generated by scripts), the name and role can be programmatically determined; states, properties, and values that can be set by the user can be programmatically set; and notification of changes to these items is available to user agents, including assistive technologies. (Level A)  & \CheckmarkBold & Aria roles and markers are set \eoline
\end{longtable}

\section{Authoring Tool}
\label{Section: Conformance of Authoring Tool}
\begin{longtable}{|L{0.6}|L{0.03}|L{0.28}|}
\caption{\label{table: authoring tool conformance}Conformance to WCAG 2.0 Guidelines for the Authoring Tool} \\
\hline \textbf{Standard} & \rot{\textbf{Pass }} & \textbf{Comment}\\ \hhline{|===|} \endhead
\multicolumn{3}{c}{Continues on the next page...} \endfoot
\endlastfoot
\textbf{1.1 Text Alternatives:} Provide text alternatives for any non-text content so that it can be changed into other forms people need, such as large print, braille, speech, symbols or simpler language. & \XSolidBrush & There is no text alternative for the video. As the video is uploaded by the user this should not be an issue.\eoline
\textbf{1.2 Time-based Media:} Provide alternatives for time-based media. & \XSolidBrush & There are no captions for the video content. This is down to the video uploaded by the user.\eoline
\textbf{1.3.1 Info and Relationships:} Information, structure, and relationships conveyed through presentation can be programmatically determined or are available in text. (Level A) & \CheckmarkBold & Sensible linear read order identified by the WAVE toolbar\footnote{\url{https://wave.webaim.org/toolbar/} (Accessed: 15 Jan 15)} \eoline
\textbf{1.3.2 Meaningful Sequence:} When the sequence in which content is presented affects its meaning, a correct reading sequence can be programmatically determined. (Level A)& \CheckmarkBold & Sensible linear read order identified by the WAVE toolbar\eoline
\textbf{1.3.3 Sensory Characteristics:} Instructions provided for understanding and operating content do not rely solely on sensory characteristics of components such as shape, size, visual location, orientation, or sound. (Level A) & \CheckmarkBold & All instructions are in a textual format \eoline
\textbf{1.4.1 Use of Color:} Color is not used as the only visual means of conveying information, indicating an action, prompting a response, or distinguishing a visual element. (Level A) & \XSolidBrush & The heat map data is only conveyed by a change in colour on the scrub bar\eoline
\textbf{1.4.2 Audio Control:} If any audio on a Web page plays automatically for more than 3 seconds, either a mechanism is available to pause or stop the audio, or a mechanism is available to control audio volume independently from the overall system volume level. (Level A) & \CheckmarkBold & Video content is paused by default and has a play/pause button\eoline
\textbf{1.4.3 Contrast (Minimum):} The visual presentation of text and images of text has a contrast ratio of at least 4.5:1, except for the following: (Level AA) 
\begin{itemize}
\item Large Text: Large-scale text and images of large-scale text have a contrast ratio of at least 3:1;
\item Incidental: Text or images of text that are part of an inactive user interface component, that are pure decoration, that are not visible to anyone, or that are part of a picture that contains significant other visual content, have no contrast requirement.
\item  Logotypes: Text that is part of a logo or brand name has no minimum contrast requirement.
\end{itemize}
 & \XSolidBrush & All of the editable colours are of an acceptable contrast ratio but the select highlight colour is not alterable. This element would need to be switched for a completely different element\eoline
\textbf{1.4.4 Resize text:} Except for captions and images of text, text can be resized without assistive technology up to 200 percent without loss of content or functionality. (Level AA) & \CheckmarkBold & Text reflows well. Some buttons are outside their boundaries\eoline
\textbf{1.4.5 Images of Text:} If the technologies being used can achieve the visual presentation, text is used to convey information rather than images of text except for the following: (Level AA)
\begin{itemize}
\item Customizable: The image of text can be visually customized to the user's requirements;
\item Essential: A particular presentation of text is essential to the information being conveyed.
\end{itemize}
Note: Logotypes (text that is part of a logo or brand name) are considered essential.
& \CheckmarkBold & All text is customisable\\ \hhline{|===|}
\textbf{2.1.1 Keyboard: }All functionality of the content is operable through a keyboard interface without requiring specific timings for individual keystrokes, except where the underlying function requires input that depends on the path of the user's movement and not just the endpoints. (Level A) & \CheckmarkBold & All components are accessible from the keyboard \eoline
\textbf{2.1.2 No Keyboard Trap: }If keyboard focus can be moved to a component of the page using a keyboard interface, then focus can be moved away from that component using only a keyboard interface, and, if it requires more than unmodified arrow or tab keys or other standard exit methods, the user is advised of the method for moving focus away. (Level A)  & \CheckmarkBold & There are no tab loops\eoline
\textbf{2.1.3 Keyboard (No Exception): }All functionality of the content is operable through a keyboard interface without requiring specific timings for individual keystrokes. (Level AAA)   & \CheckmarkBold & None of the keyboard combinations require specific timing\eoline
\textbf{2.2 Enough Time: }Provide users enough time to read and use content. & \CheckmarkBold & Level AAA as no user interactions are time sensitive \eoline
\textbf{2.3 Seizures: }Do not design content in a way that is known to cause seizures.  & \CheckmarkBold & There is no flickering content\eoline
\textbf{2.4.1 Bypass Blocks: }A mechanism is available to bypass blocks of content that are repeated on multiple Web pages. (Level A)  & \CheckmarkBold & There is only one webpage \eoline
\textbf{2.4.2 Page Titled:} Web pages have titles that describe topic or purpose. (Level A) & \CheckmarkBold & The page is titled\eoline
\textbf{2.4.3 Focus Order:} If a Web page can be navigated sequentially and the navigation sequences affect meaning or operation, focusable components receive focus in an order that preserves meaning and operability. (Level A)  & \CheckmarkBold & The tab order is the same as the programatically determined read order \eoline
\textbf{2.4.4 Link Purpose (In Context): }The purpose of each link can be determined from the link text alone or from the link text together with its programmatically determined link context, except where the purpose of the link would be ambiguous to users in general. (Level A) & \CheckmarkBold & There are no links on the page\eoline
\textbf{2.4.5 Multiple Ways:} More than one way is available to locate a Web page within a set of Web pages except where the Web Page is the result of, or a step in, a process. (Level AA)  & \CheckmarkBold & There site is all on one page\eoline
\textbf{2.4.6 Headings and Labels:} Headings and labels describe topic or purpose. (Level AA)  & \CheckmarkBold & The page has a logical heading and the sections are also headed\eoline
\textbf{2.4.7 Focus Visible:} Any keyboard operable user interface has a mode of operation where the keyboard focus indicator is visible. (Level AA)  & \CheckmarkBold & Focus is made obvious e.g. buttons have a thick dotted line around them when in focus \eoline
\textbf{2.4.8 Location: }Information about the user's location within a set of Web pages is available. (Level AAA)  & \CheckmarkBold & This is a one page application \eoline
\textbf{2.4.9 Link Purpose (Link Only): }A mechanism is available to allow the purpose of each link to be identified from link text alone, except where the purpose of the link would be ambiguous to users in general. (Level AAA)  & \CheckmarkBold & No links in the page\eoline
\textbf{2.4.10 Section Headings: }Section headings are used to organize the content. (Level AAA)
\begin{itemize}
\item Note 1: "Heading" is used in its general sense and includes titles and other ways to add a heading to different types of content.
\item Note 2: This success criterion covers sections within writing, not user interface components. User Interface components are covered under Success Criterion 4.1.2.
\end{itemize}
& \CheckmarkBold & Each section (accordion) panel has a heading\\ \hhline{|===|}
\textbf{3.1.1 Language of Page:} The default human language of each Web page can be programmatically determined. (Level A) & \CheckmarkBold & The HTML \texttt{lang} attribute is set to \texttt{en}\eoline
\textbf{3.2.1 On Focus:} When any component receives focus, it does not initiate a change of context. (Level A) & \CheckmarkBold & No change of focus when components receive focus\eoline
\textbf{3.2.2 On Input:} Changing the setting of any user interface component does not automatically cause a change of context unless the user has been advised of the behavior before using the component. (Level A) & \CheckmarkBold & Changing settings does not change the context \eoline
\textbf{3.2.3 Consistent Navigation: }Navigational mechanisms that are repeated on multiple Web pages within a set of Web pages occur in the same relative order each time they are repeated, unless a change is initiated by the user. (Level AA)  & \CheckmarkBold & This is a one page application \eoline
\textbf{3.2.4 Consistent Identification: }Components that have the same functionality within a set of Web pages are identified consistently. (Level AA)  & \CheckmarkBold & This is a one page application \eoline
\textbf{3.2.5 Change on Request: }Changes of context are initiated only by user request or a mechanism is available to turn off such changes. (Level AAA) & \CheckmarkBold & No changes of context\eoline
\textbf{3.3.1 Error Identification:} If an input error is automatically detected, the item that is in error is identified and the error is described to the user in text. (Level A)& \XSolidBrush & No error messages \eoline
\textbf{3.3.2 Labels or Instructions:} Labels or instructions are provided when content requires user input. (Level A)& \CheckmarkBold & Instructions or labels are provided\eoline
\textbf{3.3.3 Error Suggestion:} If an input error is automatically detected and suggestions for correction are known, then the suggestions are provided to the user, unless it would jeopardize the security or purpose of the content. (Level AA)& \XSolidBrush & No suggestions for input errors detected\eoline
\textbf{3.3.4 Error Prevention (Legal, Financial, Data): }For Web pages that cause legal commitments or financial transactions for the user to occur, that modify or delete user-controllable data in data storage systems, or that submit user test responses, at least one of the following is true: (Level AA)
\begin{itemize}
\item Reversible: Submissions are reversible.
\item Checked: Data entered by the user is checked for input errors and the user is provided an opportunity to correct them.
\item Confirmed: A mechanism is available for reviewing, confirming, and correcting information before finalizing the submission.
\end{itemize}
& - & N/A\\ \hhline{|===|}
\textbf{4.1.1 Parsing:} In content implemented using markup languages, elements have complete start and end tags, elements are nested according to their specifications, elements do not contain duplicate attributes, and any IDs are unique, except where the specifications allow these features. (Level A) & \CheckmarkBold & HTML validates correctly \eoline
\textbf{4.1.2 Name, Role, Value:} For all user interface components (including but not limited to: form elements, links and components generated by scripts), the name and role can be programmatically determined; states, properties, and values that can be set by the user can be programmatically set; and notification of changes to these items is available to user agents, including assistive technologies. (Level A) & \CheckmarkBold & ARIA roles and states are set where appropriate \eoline
\end{longtable}
\todo{Add error messages for invalid input?}