%% ----------------------------------------------------------------
%% Overlay.tex
%% ---------------------------------------------------------------- 
\chapter{Overlay - vgQuestions} \label{Chapter:Overlay}

\todo{I am not sure what the following list is trying to convey, should it be
removed?}
The overlay was built up in stages:
\begin{enumerate}
\item Getting an overlay to appear at a set time
\item Adding in question types
\item Allowing custom question sets to be used
\item Returning the answers to a server
\end{enumerate}

\section{Annotations}
\label{Section:Annotations}

One of the main issues to address early on was how to represent the quiz and
poll questions. The \gls{QTI} specification was
investigated, but was found to be complicated and incomplete \todo{What does
incomplete mean here?} for the project needs. It was decided to design a new
format for representing the data and logic that is used for a particular
application of videogular-questions.

This new format separates the front end of the library (responsible for
interacting with the \gls{DOM}), from the data and logic regarding the questions by
means of a message passing interface. This is achieved in a rigorous way in the
browser by means of a \gls{webworker}. This is a sandboxed separate thread that runs
in the background of the webpage. They run independently of standard user-space
scripts.  More can be found out about their use within this project in Section
BLAH \todo{Write and autoref this section}.

Using JavaScript, rather than a pure data representation (e.g. JSON or XML)
allows for the use of JavaScript to provide the logic. This makes it extremely
flexible and concise, and the isolation provided by the \gls{webworker} mitigates
many security concerns with having an application that executes data given as
input as code.

\begin{lstlisting}[language=javascript,caption={\label{code:questionworker} Code for loading an annotation}]
importScripts("../questions-worker.js");

loadAnnotations({
  "first-annotation": {
    // the time that this annotation will show up
    // (in seconds from the start of the video)
    time: 1,
    items: [
      {
        id: "first-question",
        type: "single",
        question: "What is the moon made of?",
        options: [
          {
            name: "cheese"
          },
          {
            name: "cheeese"
          },
          {
            name: "cheeeeeese"
          }
        ],
        correctAnswer: "cheese"
      },
      {
        id: "check-question",
        type: "single",
        question: "Answer incorrect, do you want to review the video",
        options: [
          {
            name: "Yes"
          },
          {
            name: "No"
          }
        ],
        action: function(questions, video) {
          if (questions.get("check-question").response === "Yes") {
            video.setTime(0);
          }
        },
        condition: function(questions) {
          return questions.get("first-question").isNotCorrect();
        }
      }
    ]
  }
});
\end{lstlisting}

Every item in an annotation can have an action and condition function. The
action function is called when a item finishes. The action function is given
the state of the annotations, such that it can make decisions and then affect
the state of the video accordingly. For example, in the above example, this is
used to only have the "skip back" question show, if the answer given to the
previous question is incorrect.

The condition function is called to determine if the respective item will show.
By default, when an annotation is shown, each item is shown in sequence.
However, if an item has a condition function, this is evaluated, and the item
only shown if the condition function returns true. If the condition function
returns false, the item is skipped. This functionality is used in the above
example to have the video skip back if the user wants it to.


An early decision was to define the difference between a poll and a quiz
question. It was decided that a poll is a type of quiz question that does not
have a correct answer.

Initially basic question types (single choice, multiple choice and scale
questions) were focused on. A variety of visualisations was implemented
including check boxes, radio buttons and sliding scales. Validation was needed
to ensure that the specified minimum and maximum limits were followed.

By having a standard schema that uses JavaScript functions it was possible to
write template functions that could be outputted from the authoring tool and
read by the overlay correctly.

\section{Front End}
\label{Section:Front end}

The appearance of the overlay depends on the question type to be shown. The
layout of these different types was carefully considered for accessibility and
ease of use. Mockups were made and user studies were done in collaboration with
a third year project student.

A set of example \gls{CSS} files are supplied with the project that layout the
questions according to the feedback received. Developers using any part of the
project can use these styles as is, or modify/develop their own.

\section{Back End}
\label{Section:Back end}

\subsection{Web Workers}
\label{Subsection:WebWorkers}

Web workers give a good way of running (sandboxed) background scripts that are
computationally intensive. They are a way of multithreading - allowing multiple
scripts to run simultaneously, avoiding the problem of unresponsive pages due
to long running scripts. This is done by using message passing.

For example, when an answer is submitted by the user this would sent a message
to the \gls{webworker} containing the answer. The \gls{webworker} can then process this
information without affecting the responsiveness of the page. Once the
processing is complete the \gls{webworker} can send a message back to the page to
tell it what to do next.

\begin{sequencediagram}
  \newthread[white]{c}{Front End}
  \newinst[4]{s}{WebWorker}

  \mess{s}{annotations}{c}

  \stepcounter{seqlevel}
  \begin{call}
    {c}{annotationStart}
    {s}{showQuestion}
  \end{call}

  \stepcounter{seqlevel}
  \begin{call}
    {c}{questionResult}
    {s}{showQuestion}
  \end{call}

  \stepcounter{seqlevel}
  \begin{call}
    {c}{questionResult}
    {s}{endAnnotation}
  \end{call}
\end{sequencediagram}

The above diagram illustrates the messages that could pass between the \gls{webworker}
, and the front end when the above example is used. Initially, the worker
sends a annotationStart message. This contains the times which annotations will
occur.

When the first time is reached, the front end sends a annotationStart
message to the worker, containing the id of that annotation. The worker then
replies with a showQuestion message, containing the contents of the first
question. Note that here, the functions are not sent to the front end, just the
JSON representation of the question is sent.

When the user responds to the question, that response is send to the worker in
a questionResult message. In this case, the user responded incorrectly,
therefore, when the \gls{webworker} evaluated the condition on the second question,
it evaluated to false. This meant that the worker replied with another
showQuestion message.

Once the user responds to the second question, the response is again sent to
the \gls{webworker}. In this case, this was the final question in the annotation, so
the worker responds with an endAnnotation message.

\section{Interaction with Analytics}
\label{Section:vgQuestions Analytics}

\todo{Move this to subsection within analytics section, add forward reference}

Since we were writing a series of plugins we wanted to ensure that no one
plugin required another to be used effectively. Instead of a custom method of
communicating between two or many possible plugins we decided to use the
publish/subscribe model to communicate with the vgAnalytics plugin.

Using the Angular broadcast system we could publish events on channels which
then would be received by anyone who subscribed to that channel.

The below code snippet shows how we communicated to the vgAnalytics plugin.

\begin{lstlisting}[language=javascript]
$rootScope.$broadcast('analytics','show_question', data);
\end{lstlisting}

Here we broadcast to the ``analytics'' channel an event with the name
``show\_question'' with the content of the data variable.

The vgAnalytics plugin listens to the ``analytics'' channel and they will
receives all messages published to this. Therefore vgQuestions can publish
information which will be received by the vgAnalytics plugin. If it has not
been instantiated then these messages will not cause any errors which is one of
the important factors in picking a communication method between the various
plugins.

By using the publish/subscribe model we can design the plugin so that if they
are both being used they will work together but have no dependencies on each
other. This allows any of our plugins to be used together or separately as the
user wishes.
